outline of questions

### 2017-04-25 analysis/first-analysis.Rmd
Files commited by wflow_commit.

---
title: "outline of questions"
author: "Wei Wang"
date: 2017-02-07
output: html_document
---

@@

$$X=  \begin{pmatrix} X_{11} & X_{12} \\ X_{21} & X_{22}  \end{pmatrix}= \left[ \begin{array}{c} U_{1} \\ U_{2} \end{array} \right] \Gamma \left[ \begin{array}{cc} V_{1}^{T}& V_{2}^{T} \end{array} \right] $$

@@

@@

\begin{eqnarray}
&\min_{U,V,\Gamma}& ||X_{11} - U_1 \Gamma V_1^T||_2 + ||X_{22} - U_2 \Gamma V_2^T||_2 \\
&st& U_1 U_1^T +  U_2 U_2^T = I \\
& & V_1 V_1^T +  V_2 V_2^T = I
\end{eqnarray}

@@

### 2 separate svd vs original svd

we know that

\begin{eqnarray}
X_{11} = U_1 \Gamma V_1^T \\
X_{22} = U_2 \Gamma V_2^T
\end{eqnarray}

but $U_1 \Gamma V_1^T$ is not SVD for $X_{11}$. On the other hand, if we combine the svd for $X_{11} = \tilde{U}_1 \Sigma_{11}\tilde{V}_1$ and that for $X_{22} = \tilde{U}_2 \Sigma_{22}\tilde{V}_2$, the combining columns $\left[ \begin{array}{c} \tilde{U}_{1} \\ \tilde{U}_{2} \end{array}  \right]$ is not the original svd $\left[ \begin{array}{c} U_{1} \\ U_{2} \end{array} \right]$. It's because $\tilde{U}_{1}$ and $\tilde{U}_{2}$ just contains local information for $X_{11}$ and $X_{22}$.

>>>>

---
title: "outline of questions"
author: "Wei Wang"
date: 2017-04-24
output: html_document
---

@@

$$X=  \begin{pmatrix} X_{00} & X_{01} \\ X_{10} & X_{11}  \end{pmatrix}= \left[ \begin{array}{c} U_{0} \\ U_{1} \end{array} \right] \Sigma \left[ \begin{array}{cc} V_{0}^{T}& V_{1}^{T} \end{array} \right] $$

@@

This is one of the old quesitons and I think I would like to keep this question.

@@

\begin{eqnarray}
&\min_{U,V,\Sigma}& ||X_{01} - U_0 \Sigma V_1^T||_2 + ||X_{10} - U_1 \Sigma V_0^T||_1 \\
&st& ||X_{00} - U_0 \Sigma V_0^T||_2 + ||X_{11} - U_1 \Sigma V_1^T||_1 = 0\\
&& U_1 U_1^T +  U_0 U_0^T = I \\
& & V_1 V_1^T +  V_0 V_0^T = I
\end{eqnarray}

@@

Maybe this is too ambitious? __Let's start from a simple toy example to check if it is possible.__

### 2 toy example with low rank assumption

#### 2.1  2 by 2 case

Here we take the simpliest example: 2 by 2 matrix $\begin{pmatrix} a & b \\ c & d  \end{pmatrix}$

#### 2.1.1 BCV in 2 by 2 case

In the original BCV frame work, we can use $||A - B D_k^+C||_F^2$ as objective function.

As I understand here, in the simpliest case, $\begin{pmatrix} a & b \\ c & d  \end{pmatrix}$ is $2 \times 2$ matrix and we assume the this matrix is a rank one matrix. So we can use $a = bd^{-1}c$ to "impute" (or "predict") the value of $a$.

For example, we know the the matrix is $\begin{pmatrix} a & 3 \\ 2 & 3  \end{pmatrix}$ with rank one, so we know $a = 2$.

#### 2.1.1 OCV in 2 by 2 case

What if we hold out two parts $b,c$ and once and hold out $a,b$ in the other time? This goes to two separate problems:

- (2.1) For holding out $b,c$:

If the matrix looks like $\begin{pmatrix} 2 & b \\ c & 3  \end{pmatrix}$ with rank one, we actually have more than one solutions.

- (2.2) For holding our $a,d$:

If the matrix looks like $\begin{pmatrix} a & 3 \\ 2 & d  \end{pmatrix}$ with rank one, we actually have more than one solutions.

When we try to solve the two problems (2.1), (2.2) separately, it seems there is no gain from the hold out pattern.

But what if we solve the together as we discussed previously on Orthogonal Cross Validation (OCV)?

#### 2.2 Orthogonal Cross Validation (background)

In OCV, we hold out each orthogonal part, and then take the average of MSE of the prediction and the hold out data, we take 3-fold as example:

```{r,echo=F}
cross_plot = function(Y,k_fold = 3){
  N = dim(Y)[1]
  P = dim(Y)[2]
  colindex = matrix(sample(P,P),ncol = k_fold)
  rowindex = matrix(sample(N,N),ncol = k_fold)

  missing= array(0,dim = c(k_fold,N,P))
  foldindex = array(0,dim = c(k_fold,k_fold,2))
  for(i in 1:k_fold){
    for(j in 1:k_fold){
      foldindex[i,j,1] = i
      foldindex[i,j,2] = (i+j) %% k_fold
    }
  }
  foldindex[which(foldindex == 0)] = k_fold
  for(i in 1:k_fold){
    missing[i, , ] = Y
    for(j in 1:k_fold){
      missing[i,rowindex[,foldindex[j,i,1]],colindex[,foldindex[j,i,2]]] = NA
    }
  }
  par(mfrow = c(2,2), mar = (c(5,4,4,2)-1.9))
  image(Y,main = "data Y")
  for(i in 1:k_fold){
    image(missing[i,,],main = "missing data")
  }
  return(missing)
}

N = 3
P = 3
Y = matrix(rep(1,N*P),ncol =  P)
g = cross_plot(Y)
```

$$Y = \begin{pmatrix} Y_{11} & Y_{12} & Y_{13} \\ Y_{21} & Y_{22} & Y_{23} \\ Y_{31} & Y_{32} & Y_{33} \end{pmatrix}= \begin{pmatrix} Y_{(1)} & Y_{(2)} & Y_{(3)} \\ Y_{(3)} & Y_{(1)} & Y_{(2)} \\ Y_{(2)} & Y_{(3)} & Y_{(1)} \end{pmatrix}$$

by letting $Y_{(1)} = \{  Y_{11},  Y_{22} , Y_{33}\}$, $Y_{(2)} = \{  Y_{12},  Y_{23} , Y_{31}\}$ and $Y_{(3)} = \{  Y_{13},  Y_{21} , Y_{32}\}$, which are orthogonal to each other.

Then the MSE for each row and column permutation would be:

\begin{eqnarray}
MSE &=& MSE_1 + MSE_2 + MSE_3\\
 &=& ||\hat{Y}_{(1)} - Y_{(1)}||_2 + ||\hat{Y}_{(2)} - Y_{(2)}||_2 + ||\hat{Y}_{(3)} - Y_{(3)}||_2
\end{eqnarray}

#### 2.3 2 by 2 matrix again

Let's go back to 2 by 2 case:

The question is can we get better idea by solving problem (2.1) and (2.2) together (by taking the average of MSE)?

So I would guess that the problem goes to:

\begin{eqnarray}
& & \min_{u,v,\lambda} MSE_1 + MSE_2\\
&s.t.& uu^T = I\\
&& v v^T = I \\
&& \lambda >0 \\
&where& MSE_1 = ||a - u_0\lambda v_0||_F + ||d - u_1 \lambda v_1||_F\\
&and& MSE_2 = ||b - u_0\lambda v_1||_F + ||c - u_1 \lambda v_0||_F
\end{eqnarray}

with assumption the $\begin{pmatrix} a & b \\ c & d  \end{pmatrix}$ is rank one matrix and SVD is as $$\begin{pmatrix} a & b \\ c & d  \end{pmatrix} = u\lambda v^T$$

**So we can see that SVD solution is the solution of our problem. What's more, in this simple example, we might be able to find rank two solution which BCV can't.**
